POPLMark goes Concurrent!\\Challenge problems for process calculi and behavioural types

### 2023-09-26 challenges.tex
Fix explanation of two-level syntax.

\subsubsection{Syntax}
In this section we assume that \emph{names}  can be compared for equality.
The syntax in this challenge will be split into two levels: processes and summations.
The syntax of processes is given by:
\begin{align*}
  P,Q :=&&& \Ppar{P}{Q} \\
  |&&& \Pres{x}{P} \\
  |&&& M
\end{align*}
The syntax of summations is given by:
\begin{align*}
  M,N :=&&& \Pend \\
  |&&& \Pout{x}{y}{P} \\
  |&&& \Pin{x}{y}{P} \\
  |&&& \Pchoice{M}{N}
\end{align*}
Splitting the syntax into these two layers has the effect of forcing choices to be guarded by an input or an output, which simplifies the theory.
Allowing choices between arbitrary processes is rarely useful.

>>>>

\subsubsection{Syntax}
In this section we assume that \emph{names}  can be compared for equality.
The syntax in this challenge will be split into two levels: processes and summations.
The syntax of processes is given by:
\begin{align*}
  P,Q :=&&& \Ppar{P}{Q} \\
  |&&& \Pres{x}{P} \\
  |&&& M
\end{align*}
The syntax of summations is given by:
\begin{align*}
  M,N :=&&& \Pend \\
  |&&& \Pout{x}{y}{P} \\
  |&&& \Pin{x}{y}{P} \\
  |&&& \Pchoice{M}{N}
\end{align*}
Splitting the syntax into these two layers has the effect of disallowing choices directly between parallel processes.
Allowing choices between arbitrary processes complicates the theory and is rarely useful.
